The eclipse of ASASSN-21qj

### 2022-09-16 src/tex/ms.tex
[showyourwork] overleaf sync

>>>>

\textcolor{magenta}{\textbf{Complementary to white dwarf star pollution.}}
\textcolor{magenta}{Probing disintegrating planetary material is the only method to access the composition of building blocks of planets outside of the Solar System. E.g. the disintegration of a gas giant around a white dwarf was used to infer its composition \citep{Gaensike2019}. White dwarf star pollution has also yielded valuable insights about refractory (Fe/Mgxxx) element content of rocky  material (REFs). MORE XXX.}

\textcolor{magenta}{Planets and asteroids falling into white dwarfs are, however, haven been probably heavily processed during the late stellar evolution as the host star became a red gianr before evolving into a white dwarf (REFs). The unusually warm (how much?) debris disk passing in front of a young star may allow to directly probe the interior of planetisimals during the early stages of planet formation. The eclipse is expected to last for xxx days, allowing to perform further spectroscopic analysis of the dust in this system.}
